Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Polish "Markup for properties"

\noindent To specify properties, we also propose new markup. In this paper, we
use the {\tt prop>} prefix. We can write non-quantified properties as follows:

@@

\noindent And it is possible to quantify properties by using a
lambda expression. The property from Section~\ref{sec:doctest-haddock}
can be written as:

@@

\noindent Note that the $\hookleftarrow$ symbol denotes line
continuation.
If a default type is not suitable, expression type-signatures can be
specified for each parameter:

@@

\noindent Since the right hand side of {\tt ->} is verbose as documentation,
lambda terms without the lambda prefix are also allowed:

@@

\noindent We call such properties \emph{implicitly quantified}.  The
given property is implicitly quantified over \verb|xs|.

>>>>

\noindent To specify properties, we also introduce new markup. A line
starting with ``{\tt prop>}'' indicates a property.

@@

\noindent It is possible to quantify properties by using a
lambda expression. The property from Section~\ref{sec:doctest-haddock}
can be written as:

@@

\noindent The $\hookleftarrow$ symbol denotes line continuation.

GHCi's type defaulting~\cite{ghc-manual} applies to properties.  If a default type is
not suitable explicit type-signatures can be used:

\begin{quote}
    TBD: @kazu, can you add this to the bib:
    \url{http://www.haskell.org/ghc/docs/7.4.1/html/users_guide/interactive-evaluation.html}
\end{quote}

@@

\noindent Since the lambda abstraction adds nothing to the
documentation, it can be omitted:

@@

\noindent We call such properties \emph{implicitly quantified}.  The
given property is implicitly quantified over {\tt xs}.
